Automatic conversion of colloquial Finnish to standard Finnish

### 2015-02-02 2015-nodalida-finnormal/finnormal2015.tex
move dir
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58647 72bbbca6-d526-0410-a7d9-f06f51895060

The systems for normalisation are able to improve out-of-vocabulary rates in 
many cases, most likely as the online statistical system that we used is trained
on more formal texts. Frequent contractions such as \emph{onks?} `is there?',
\emph{oo} `not' and \emph{vaa} `only' are found untranslated in the output, but 
are easily converted by the systems.

>>>>

The systems for normalisation are able to improve out-of-vocabulary rates in 
many cases, most likely as the online statistical system that we used is trained
on more formal texts. Frequent contractions such as \emph{onks?} `is there?',
\emph{oo} `be.{\sc conneg}'\footnote{The word \emph{oo} is the negative form of the verb \emph{olla} `to be' in Finnish.} and \emph{vaa} `only' are found untranslated in the output, but 
are easily converted by the systems.
